Behavior Driven Development in Haskell

### 2012-10-20 paper.tex
Getting it fast -> Making it fast (as suggested by reviewer 3)
Fix typo
Remove \titlebanner, etc.

\conferenceinfo{Haskell Symposium 2012}{13th September, Copenhagen.}
\copyrightyear{2012}
\copyrightdata{[to be supplied]}

% These are ignored, unless 'preprint' option specified.
\titlebanner{A draft paper to be submitted to Haskell Symposium 2012}
\preprintfooter{BDD in Haskell}

@@

We present a step-by-step refinement of a library, and a corresponding
spec.  Each line of code is only given once when introduced,
subsequent code fragments are incremental updates.  Appendix
\ref{sec:appendix-code} contains the complete code of this section.

@@

\subsubsection{Getting it fast}

@@

\noindent It is possible to to make this specification reusable, by
abstracting over the type:

>>>>

%\conferenceinfo{Haskell Symposium 2012}{13th September, Copenhagen.}
\copyrightyear{2012}
\copyrightdata{[to be supplied]}

% These are ignored, unless 'preprint' option specified.
%\titlebanner{A draft paper to be submitted to Haskell Symposium 2012}
\preprintfooter{BDD in Haskell}

@@

We present a step-by-step refinement of a library, and a corresponding
spec.  Each line of code is only given once when introduced,
subsequent code fragments are incremental updates, import statements
are omitted.  Appendix
\ref{sec:appendix-code} contains the complete code of this section.

@@

\subsubsection{Making it fast}

@@

\noindent It is possible to make this specification reusable, by
abstracting over the type:
